Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2013-01-03 docs/tex/experiments.tex
Experiment 11. Feature space and sequence length

\subsubsection{Simulation Experiment 10: Vary Feat space }
\label{sim:featspace}
Keeping the seq space at 20, vary feat space from 5-10-25-50

\subsubsection{Simulation Experiment 11: Vary Feat space and sequence length}
\label{sim:featspacelen}
Keeping the seq space at 20, vary feat space from 5-10-25-50, sequence length from 2^2,2^16

>>>>

\subsubsection{Simulation Experiment 10: Vary Feat space }
\label{sim:featspace}
Keeping the seq space at 20 and seq len at 16. vary feat space from 5-10-25-50

sim3_featspace_5_0pareto : 0.344 seconds
sim3_featspace_5_1pareto : 0.426 seconds
sim3_featspace_5_2pareto : 0.499 seconds
sim3_featspace_10_0pareto : 0.543 seconds
sim3_featspace_10_1pareto : 0.706 seconds
sim3_featspace_10_2pareto : 0.657 seconds
sim3_featspace_25_0pareto : 0.632 seconds
sim3_featspace_25_1pareto : 0.493 seconds
sim3_featspace_25_2pareto : 0.536 seconds
sim3_featspace_50_0pareto : 0.543 seconds
sim3_featspace_50_1pareto : 0.676 seconds
sim3_featspace_50_2pareto : 0.586 seconds

\subsubsection{Simulation Experiment 11: Vary Feat space and sequence length}
\label{sim:featspacelen}
Keeping the seq space at 20, vary feat space from 5-10-25-50, sequence length from seqlen to 64.
sim3_featspacelen_4_5_0pareto : 0.030 seconds
sim3_featspacelen_4_5_1pareto : 0.037 seconds
sim3_featspacelen_4_10_0pareto : 0.046 seconds
sim3_featspacelen_4_10_1pareto : 0.045 seconds
sim3_featspacelen_4_25_0pareto : 0.056 seconds
sim3_featspacelen_4_25_1pareto : 0.037 seconds
sim3_featspacelen_4_50_0pareto : 0.028 seconds
sim3_featspacelen_4_50_1pareto : 0.071 seconds
sim3_featspacelen_16_5_0pareto : 0.338 seconds
sim3_featspacelen_16_5_1pareto : 0.419 seconds
sim3_featspacelen_16_10_0pareto : 0.536 seconds
sim3_featspacelen_16_10_1pareto : 0.699 seconds
sim3_featspacelen_16_25_0pareto : 0.621 seconds
sim3_featspacelen_16_25_1pareto : 0.515 seconds
sim3_featspacelen_16_50_0pareto : 0.584 seconds
sim3_featspacelen_16_50_1pareto : 0.752 seconds
sim3_featspacelen_32_5_0pareto : 2.014 seconds
sim3_featspacelen_32_5_1pareto : 2.501 seconds
sim3_featspacelen_32_10_0pareto : 2.142 seconds
sim3_featspacelen_32_10_1pareto : 2.176 seconds
sim3_featspacelen_32_25_0pareto : 2.277 seconds
sim3_featspacelen_32_25_1pareto : 2.080 seconds
sim3_featspacelen_32_50_0pareto : 2.555 seconds
sim3_featspacelen_32_50_1pareto : 1.944 seconds
sim3_featspacelen_64_5_0pareto : 8.940 seconds
sim3_featspacelen_64_5_1pareto : 10.489 seconds
sim3_featspacelen_64_10_0pareto : 9.777 seconds
sim3_featspacelen_64_10_1pareto : 8.458 seconds
sim3_featspacelen_64_25_0pareto : 10.321 seconds
sim3_featspacelen_64_25_1pareto : 9.168 seconds
sim3_featspacelen_64_50_0pareto : 9.095 seconds
sim3_featspacelen_64_50_1pareto : 8.893 seconds
